Dynamic Species Interactions in the San Nicolas Island Kelp Forest

### 2018-07-17 EDM_SNI_analysis.Rmd
ints multi

  # box plot of interactions
  sppname <- namekey$long[match(species,namekey$short)]
  int.box <- ggplot(coeffs.long,aes(x=plotting,y=value))+
    geom_boxplot() +
    geom_hline(yintercept=0,linetype=2,col="gray40")+
    xlab("Interacting Variable") +
    ylab("Coefficient") +
    ggtitle(paste("Interactive Effects on Dynamics of ",sppname))

@@

>>>>

  # box plot of interactions
  sppname <- species
  int.box <- ggplot(coeffs.long,aes(x=plotting,y=value))+
    geom_boxplot() +
    geom_hline(yintercept=0,linetype=2,col="gray40")+
    xlab("Interacting Variable") +
    ylab("Coefficient") +
    ggtitle(paste("Interactive Effects on Dynamics of ",sppname))

@@

### Multivariate S-maps with Interactions

```{r multivariate smaps}
ints.causal.vars <- purrr::map(interaction_names, function(x) {
  interactions.xmap_rast %>%
    filter(predictee==x,!is.na(rho))->out
  out <- c(x,out$predictor)
  out
})

names(ints.causal.vars)=interaction_names

# apply s-maps
ints.multi.mods <- purrr::map(interaction_names,function(x) {
  smap_multi(interactions.block,westend.segs,x,ints.causal.vars[[x]])
})
names(ints.multi.mods) <- interaction_names
